% Created 2023-10-17 Tue 11:38
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{minted}
\usepackage[margin=0.5in]{geometry}
\usepackage[spanish, english]{babel}
\author{Agustín Alejandro Mota Hinojosa}
\date{\today}
\title{1-2 Benefits of PL/SQL}
\hypersetup{
 pdfauthor={Agustín Alejandro Mota Hinojosa},
 pdftitle={1-2 Benefits of PL/SQL},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.1 (Org mode 9.7)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

\section*{Vocabulary}
\label{sec:org2071523}

Match key terms of terminology at the end of this lesson slides with its definition.
Identify the vocabulary word for each definition below:

\begin{enumerate}
\item The ability for PL/SQL programs to run anywhere an Oracle server runs?

\textbf{Portability}

\item The basic unit of PL/SQL programs- also known as modules

\textbf{Block}

\item An error that occurs in the database or in a user’s program during runtime.

\textbf{Exception}
\end{enumerate}
\section*{Solve it}
\label{sec:orgcee713a}

\begin{enumerate}
\item Why is it more efficient to combine SQL statements into PL/SQL blocks?

Combining SQL statements into PL/SQL blocks is more efficient because it
reduces the overhead of sending multiple SQL statements to the database
server.

\item Why is it beneficial to use PL/SQL with an Oracle database? List at least
three reasons.

\begin{enumerate}
\item Tight Integration: PL/SQL is tightly integrated with Oracle, allowing
for seamless interaction with the database.

\item Performance: PL/SQL provides better performance optimization and
reduces the need for frequent client-server communication.

\item Security: PL/SQL allows for fine-grained access control and enhances
database security.
\end{enumerate}

\item How is PL/SQL different from C and Java? List three differences.

PL/SQL is primarily used for database programming and stored procedures,
while C and Java are general-purpose programming languages.

\item List three examples of what you can build with PL/SQL code.

\begin{enumerate}
\item Stored Procedures and Functions

\item Triggers

\item Data transformation
\end{enumerate}
\end{enumerate}
\end{document}